\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-5pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeItemPlain}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nisargi Shah}} & Email: \href{mailto:nisargi3112@gmail.com}{nisargi3112@gmail.com}\\
  \href{https://www.linkedin.com/in/nisargi-shah/}{linkedin.com/in/nisargi-shah} $|$ Navi Mumbai, India & Mobile: +91-9825839118 \\
\end{tabular*}

%----------SUMMARY-----------------
\section{Summary}
\small{Data-focused Analyst at Reliance Industries building predictive-maintenance and asset-analytics solutions for industrial IoT --- failure prediction, anomaly detection, and MLOps-backed deployments across 150,000+ assets. Former Data Science Intern at ISRO with hands-on experience in Python, ML modeling, and large-scale geospatial data pipelines.}

%----------EDUCATION---------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Pandit Deendayal Energy University (PDEU)}{Gandhinagar, Gujarat}
    {B.Tech in Computer Science; CGPA: 9.31}{Sep 2021 -- May 2025}
\resumeSubHeadingListEnd

%----------EXPERIENCE--------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Reliance Industries Limited}{Navi Mumbai, Maharashtra}
    {Analyst -- Digital \& IoT, Asset Reliability}{Aug 2025 -- Present}
    \resumeItemListStart
      \resumeItem{GT Health Monitoring (Failure Prediction \& Anomaly Detection)}
        {Drove the complete lifecycle --- requirement gathering through final deployment --- of an in-house gas-turbine health monitoring product built on failure-prediction and anomaly-detection models with an MLOps pipeline; provides 3--8 days advance warning of equipment failures, preventing unplanned outages and production losses.}
      \resumeItem{Early Event Detection (EED)}
        {Analyze model outputs from a predictive analytics system covering 1,000 critical rotary assets, translating predictions into actionable early-failure notifications (3--8 days ahead) for site reliability teams.}
      \resumeItem{Asset Performance Management (GE Vernova)}
        {Manage asset-health data on GE Vernova's APM platform for 150,000+ assets across 10 sites; core team member overseeing GE's APM software upgrade.}
      \resumeItem{IoT Instrumentation Analytics}
        {Lead analytics on 3 IoT projects instrumenting $\sim$80 rotary assets across 3 sites, improving sensor-reading accuracy and reducing manual data collection and equipment downtime.}
      \resumeItem{MTBF Dashboard}
        {Built a Mean-Time-Between-Failures dashboard consolidating asset-level incident data to track reliability metrics and failure rates across multiple sites.}
    \resumeItemListEnd

  \resumeSubheading
    {Space Application Centre, ISRO}{Ahmedabad, Gujarat}
    {Data Science Intern}{Jan 2025 -- May 2025}
    \resumeItemListStart
      \resumeItem{Satellite Imagery Data Pipeline}
        {Developed an end-to-end, reproducible Python pipeline for satellite imagery processing and geospatial analysis --- soil-moisture estimation, feature extraction, and spatial validation at 100\,m resolution --- supporting research and upcoming satellite missions. \textit{Stack: Python, QGIS, Rasterio, GDAL, NumPy, GeoPandas, Matplotlib.}}
    \resumeItemListEnd

  \resumeSubheading
    {AM/NS India Limited}{Surat, Gujarat}
    {Web Development Intern}{Jun 2023 -- Jul 2023}
    \resumeItemListStart
      \resumeItem{Full-Stack Development}
        {Enhanced an employee notification system: redesigned the frontend, built Django REST services, and automated company-wide email workflows.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------PROJECTS----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{Air-Traffic Delay Prediction (COVID Impact Study)}
    {Built ML models to predict U.S. air-traffic delays and conducted a comparative business-impact analysis of pre-COVID vs COVID-era operations, translating predictions into operational insights for aviation.}
  \resumeSubItem{Bone Fracture Detection from X-ray Images}
    {Developed and deployed an ML-based fracture detection system with an intuitive interface for real-world diagnostic support.}
  \resumeSubItem{Health \& Fitness Tracker}
    {Built a Flask platform tracking calories, BMI, workouts, and activity, with personalized recommendations via web scraping.}
\resumeSubHeadingListEnd

%----------SKILLS------------------
\section{Skills}
\resumeSubHeadingListStart
  \resumeItemPlain{\textbf{Languages}: Python, SQL, C, JavaScript}
  \resumeItemPlain{\textbf{ML \& Analytics}: Predictive Maintenance, Failure Prediction, Anomaly Detection, MLOps workflows, NumPy, Pandas, Matplotlib, GeoPandas}
  \resumeItemPlain{\textbf{BI \& Visualization}: Power BI, Tableau}
  \resumeItemPlain{\textbf{Databases}: MySQL, Microsoft SQL Server, MongoDB, Azure Data Lake}
  \resumeItemPlain{\textbf{Geospatial}: QGIS, Rasterio, GDAL}
  \resumeItemPlain{\textbf{Tools \& Cloud}: Git, Docker, AWS, Azure}
\resumeSubHeadingListEnd

%----------CERTIFICATIONS----------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeItemPlain{\textbf{Google Cloud GenAI Fundamentals} --- February 2024}
  \resumeItemPlain{\textbf{Goldman Sachs Software Engineering Virtual Experience Program} --- February 2024}
\resumeSubHeadingListEnd

%----------ADDITIONAL--------------
\section{Additional Information}
\resumeSubHeadingListStart
  \resumeItemPlain{\textbf{Achievements}: International Rank 53, Mathematics Olympiad; Editor-in-Chief, department newsletter; hackathon participant}
  \resumeItemPlain{\textbf{Languages}: English, Hindi, Gujarati (fluent); French (b